\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-19 paper.qmd
Added intro for tuning

### Measuring the fit
 <!-- Fitted values,  Error calculation-->

@@

### Tuning

<!-- removal of low density bins, removing long edges, choice of bins-->

>>>>

### Measuring the fit {#sec-summary}
 <!-- Fitted values,  Error calculation-->

@@

### Tuning
<!-- removal of low density bins, removing long edges, choice of bins-->

The performance and robustness of our model depend on three key parameters: (i) the total number of bins ($b$), (ii) a benchmark value used to remove low-density hexagons, and (iii) a benchmark value used to remove long edges. However, there is no analytical formula to calculate an appropriate value for these parameters. The selection of these parameter values depends on the model performance computed by MSE (see @sec-summary).

#### Choice of bins

The number of hexagonal bins in the hexagonal grid has a considerable impact on the construction of the \gD{} model, serving as the initial step. The chosen total number of bins must effectively capture the structure of the NLDR data. If the number of bins is too low, the model may not be able to capture the structure of the NLDR data effectively (see @fig-binsize (a)), while if there are too many bins, it may result in over-fitting the individual points of the NLDR data (see @fig-binsize (c)). Therefore, it is important to determine an appropriate number of bins to construct an effective model.

<!--add three choice of bins-->

Furthermore, the total number of bins is calculated based on the number of bins along the x-axis and y-axis, $b = b_1 \times b_2$. To determine the effective $b$, candidate values are selected based on the range between the minimum and approximate maximum $b_1$, because $b_2$ is computed from $b_1$. The minimum $b_1$ is set to $2$, while the maximum number is estimated by taking the square root of $n$. The analysis evaluates the MSE across varying $b$ within this range, covering the minimum to maximum values along both axes (see @fig-diagnostic1-scurve).

<!--add MSE vs total number of error plot-->

#### Removal of low density bins

#### Removing long edges

### 2024-05-19 paper.tex
Added intro for tuning

\subsection{Measuring the fit}\label{measuring-the-fit}

@@

To assess how well our method captures and represents the underlying
structure of the high-D data, Mean Squared Error (MSE) is used. When
computing MSE, total model error (see \textbf{?@sec-summary}) is divided
by the number of observations to make it as a mean value (see
Equation~\ref{eq-equation9}).

@@

>>>>

\subsection{Measuring the fit}\label{sec-summary}

@@

To assess how well our method captures and represents the underlying
structure of the high-D data, Mean Squared Error (MSE) is used. When
computing MSE, total model error (see Section~\ref{sec-summary}) is
divided by the number of observations to make it as a mean value (see
Equation~\ref{eq-equation9}).

@@

The performance and robustness of our model depend on three key
parameters: (i) the total number of bins (\(b\)), (ii) a benchmark value
used to remove low-density hexagons, and (iii) a benchmark value used to
remove long edges. However, there is no analytical formula to calculate
an appropriate value for these parameters. The selection of these
parameter values depends on the model performance computed by MSE (see
Section~\ref{sec-summary}).

\subsubsection{Choice of bins}\label{choice-of-bins}

The number of hexagonal bins in the hexagonal grid has a considerable
impact on the construction of the \gD{} model, serving as the initial
step. The chosen total number of bins must effectively capture the
structure of the NLDR data. If the number of bins is too low, the model
may not be able to capture the structure of the NLDR data effectively
(see \textbf{?@fig-binsize} (a)), while if there are too many bins, it
may result in over-fitting the individual points of the NLDR data (see
\textbf{?@fig-binsize} (c)). Therefore, it is important to determine an
appropriate number of bins to construct an effective model.

Furthermore, the total number of bins is calculated based on the number
of bins along the x-axis and y-axis, \(b = b_1 \times b_2\). To
determine the effective \(b\), candidate values are selected based on
the range between the minimum and approximate maximum \(b_1\), because
\(b_2\) is computed from \(b_1\). The minimum \(b_1\) is set to \(2\),
while the maximum number is estimated by taking the square root of
\(n\). The analysis evaluates the MSE across varying \(b\) within this
range, covering the minimum to maximum values along both axes (see
\textbf{?@fig-diagnostic1-scurve}).

\subsubsection{Removal of low density
bins}\label{removal-of-low-density-bins}

\subsubsection{Removing long edges}\label{removing-long-edges}
